### 2015-02-20 prelim.tex
Added error kernel to prelim, layout for additional sections set.

introduce error kernel.

 polynomial spaces,

introduce notion of decay.

>>>>

The error $\Ltwonorm{f - \appf{f}}$ between $f$ and its approximation
$\appf{f} \in \aspace{\lattice{L}_h}{\varphi}$ can conveniently be
quantified via an error kernel in the Fourier domain. It is defined as
\begin{equation}
  E(\vect{\omega}) := \underbrace{1 - \frac{\abs{\ft{\varphi}(\vect{\omega})}^2}{\ft{A}_{\varphi}(\vect{\omega})}}_{E_{\mathsf{min}}(\vect{\omega})}
  + 
  \underbrace{
    \ft{A}_{\varphi}(\vect{\omega})
    \abs{\ft{\analysis{\varphi}}(\vect{\omega}) -
      \ft{\dual{\varphi}}(\vect{\omega})}^2
  }_{E_{\mathsf{res}}(\vect{\omega})}.
  \label{eq:scErrorKernel}
\end{equation}
For a bandlimited function $f$ whose spectrum is entirely contained
within the Voronoi cell of $\duallattice{L}_h$ centered around
$\vect{\omega} = 0$, we have 
\begin{equation}
\Ltwonorm{f - \appf{f}} = \int_{\reel^s}
\abs{\ft{f}(\vect{\omega})}^2 E(h\vect{\omega}) d\vect{\omega},
\label{eq:avgError}
\end{equation}
whereas when $f \in W_2^k(\reel^s)$ with $k > \frac{1}{2}$, the
integral in~\eqref{eq:avgError} gives the $L_2$-error averaged over
all possible shifts of $f$. Even though this kernel was initially
proposed in the univariate setting by Blu and Unser~\cite{blu99}, multivariate
non-Cartesian extensions have also appeared in the
literature~\cite{condat05hexagonal, condat07, condat08, alim10,
  condat11}. Note that the minimum-error approximation scenario occurs
when $f$ is orthogonally projected to $\aspace{\lattice{L}_h}{\varphi}$,
or in other words $\analysis{\varphi}$ is chosen to be  $\dual{\varphi}$.
 polynomial spaces,

\subsection{Approximation Error}

### 2015-02-20 results.tex
Updating refs and splitting results
Added error kernel to prelim, layout for additional sections set.

\subsection{Experiments and Results}

\subsubsection{Cartesian Lattice}
Choosing $\mathbf{\Xii = \Xii_{C2} := \left[ I_3  \ I_3 \right]}$ (the $3 \times 6$ matrix created by the union of two identity matrices) generates a triliniear piecewise polynomial. It is easy to see, by definition, when $\mathbf{\Xii_{C2}}$ is used in conjunction with \EQp{eq:box_def}, the resulting function $M_\mathbf{\Xii_{C2}}(\vx)$ corresponds to the non-centered tensor product extension of the linear B-spline in three dimensions. Likewise, the non-centered cubic tensor product box spline is given by $M_\mathbf{\Xii_{C4}}(\vx)$, where $\mathbf{\Xii_{C4} := \left[ I_3  \ I_3 \ I_3  \ I_3 \right]}$. A box spline is easily centered by taking $M_\mathbf{\Xii}(\vx + \mathbf{c_\Xii})$, with $\mathbf{c_\Xii}:=\sum_{\xi \in \mathbf{\Xii}} \frac{1}{2}\xi$. We will assume, unless otherwise stated, that $M_\mathbf{\Xii}$ defines the centered box spline generated by $\mathbf{\Xii}$.

\subsubsection{BCC Lattice}
On the BCC lattice, a choice of {\footnotesize
\begin{equation*}
	\mathbf{\Xii_{B}} := 
	\begin{bmatrix} 
		-1 & 1 & 1 & -1 \\
		1 & -1 & 1 & -1 \\
		1 & 1 & -1 & -1 
	\end{bmatrix}
\end{equation*}}

@@

\subsubsection{Shifted Basis Functions}
We also consider shifted box splines $M_{\mathbf{\Xii}}^{\xi_i}(\vx) := M_{\mathbf{\Xii}}(\vx - \frac{1}{2}\mathbf{\xi}_i)$, where $\mathbf{\xi}_i$ is any direction vector in $\mathbf{\Xii}$. In the univariate case with linear B-splines, it has been shown that introducing a shift can offer an improvement when representing scalar data \cite{linearrev}. More generally and relevant to our purposes, they have also been shown to reduce error when approximating the gradient of scalar fields \cite{gradrev}.

@@

% This isn't true for the images that are currently in the paper.
%For our visual comparisons, we ray trace the iso-surface produced by our method. We reason that that any marching algorithm that produces a triangulated mesh, inherently uses linear interpolation to fill in missing data, and potentially reduces the approximation power of our function space. However, in order to measure the error between our reconstructions and a baseline, a mesh must be extracted. In that case we march to twice the resolution of an equivalent Cartesian grid.

@@

%- Perhaps a little more discussion on how the approach compares to Poisson and screened poisson, both quantitative and qualitative. -
Since the Gargoyle model has many interesting high frequency features, we consider reconstructing it at increasing grid resolutions. For the Poisson and Screened Poisson methods, we restrict the depth of the tree so that the finest resolution provided by the oct-tree is equivalent to that of the regular Cartesian, \FG{fig:t1}. We also seem to be able to improve upon the Screened Poisson method, however, the parameter space needs to be explored further to conclusively assert this. Regardless, it is still a good baseline with which to compare our results.

>>>>

\section{Experiments}

\subsection{Cartesian Lattice}
Blurb about cartesian lattices.

\subsubsection{Basis function}
Choosing $\mathbf{\Xii = \Xii_{C2} := \left[ I_3  \ I_3 \right]}$ (the $3 \times 6$ matrix created by the union of two identity matrices) generates a triliniear piecewise polynomial. It is easy to see, by definition, when $\mathbf{\Xii_{C2}}$ is used in conjunction with \EQp{eq:box_def}, the resulting function $M_\mathbf{\Xii_{C2}}(\vx)$ corresponds to the non-centered tensor product extension of the linear B-spline in three dimensions. Likewise, the non-centered cubic tensor product box spline is given by $M_\mathbf{\Xii_{C4}}(\vx)$, where $\mathbf{\Xii_{C4} := \left[ I_3  \ I_3 \ I_3  \ I_3 \right]}$. A box spline is easily centered by taking $M_\mathbf{\Xii}(\vx + \mathbf{c_\Xii})$, with $\mathbf{c_\Xii}:=\sum_{\xi \in \mathbf{\Xii}} \frac{1}{2}\xi$. We will assume, unless otherwise stated, that $M_\mathbf{\Xii}$ defines the centered box spline generated by $\mathbf{\Xii}$.

\subsubsection{Filter weights}

\subsection{BCC Lattice}
Blurb about cartesian lattices.

\subsubsection{Basis function}
On the BCC lattice, a choice of {\footnotesize
\begin{equation*}
	\mathbf{\Xii_{B}} := 
	\begin{bmatrix} 
		-1 & 1 & 1 & -1 \\
		1 & -1 & 1 & -1 \\
		1 & 1 & -1 & -1 
	\end{bmatrix}
\end{equation*}}

@@

\subsubsection{Filter weights}

\subsection{Shifted Basis Functions}
We also consider shifted box splines $M_{\mathbf{\Xii}}^{\xi_i}(\vx) := M_{\mathbf{\Xii}}(\vx - \frac{1}{2}\mathbf{\xi}_i)$, where $\mathbf{\xi}_i$ is any direction vector in $\mathbf{\Xii}$. In the univariate case with linear B-splines, it has been shown that introducing a shift can offer an improvement when representing scalar data \cite{linearrev}. More generally and relevant to our purposes, they have also been shown to reduce error when approximating the gradient of scalar fields \cite{gradrev}.

@@

@@

Since the Gargoyle model has many interesting high frequency features, we consider reconstructing it at increasing grid resolutions. For the Poisson and Screened Poisson methods, we restrict the depth of the tree so that the finest resolution provided by the oct-tree is equivalent to that of the regular Cartesian, \FG{fig:t1}. We also seem to be able to improve upon the Screened Poisson method, however, the parameter space needs to be explored further to conclusively assert this. Regardless, it is still a good baseline with which to compare our results.
